---
title: "Preliminary Analysis"
output:
  html_document:
    code_folding: hide
    fig_height: 12
    fig_width: 12
    toc: yes
    toc_float:
      collapsed: true
      smooth_scroll: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, cache = TRUE, cache.lazy = TRUE)
```


# Data 

```{r}
library(scater)
library(SingleCellExperiment)
library(ggthemes)
library(ggplot2)
library(ggridges)
library(plyr)
library(raster)
library(gridExtra)
library(sp)
library(spatstat)
library(uwot)
source("functions/image_analysis_function.R")
set.seed(2020)
```


## Keren et al. 


```{r}
load("../../sc-targeted-proteomics/data/mibiSCE.rda")
mibi.sce
```


```{r}
cat("Patients information")
table(mibi.sce$SampleID)

cat("Cell types informaton")
# table(mibi.sce$tumor_group)
# table(mibi.sce$immune_group)

# rename the cell types
mibi.sce$cellTypes <- ifelse(as.character(mibi.sce$immune_group) != "not immune",
                             as.character(mibi.sce$immune_group),
                             as.character(mibi.sce$tumor_group))

table(mibi.sce$cellTypes)

mibi.sce$cellTypes_group <- ifelse(as.character(mibi.sce$immune_group) != "not immune",
                                   "Micro-environment",
                                   "Tumour")

selected_chanel_mibi <- rownames(mibi.sce)[rowData(mibi.sce)$is_protein == 1]

```


```{r}
# color for mibi cell types
cellTypes_group_mibi_color <- tableau_color_pal("Tableau 10")(length(unique(mibi.sce$cellTypes_group)))
cellTypes_group_mibi_color <- c(cellTypes_group_mibi_color, "black")
names(cellTypes_group_mibi_color) <- c(unique(mibi.sce$cellTypes_group), "Background")

cellTypes_mibi_color <- tableau_color_pal("Classic 20")(length(unique(mibi.sce$cellTypes)))
cellTypes_mibi_color <- c(cellTypes_mibi_color, "black")
names(cellTypes_mibi_color) <- c(unique(mibi.sce$cellTypes), "Background")
```



Visualising all cells using UMAP

```{r}
## Dimension Reduction using UMAP
mibi.sce <- runUMAP(mibi.sce, exprs_values = "mibi_exprs", 
                    feature_set = selected_chanel_mibi)
g1 <- plotUMAP(mibi.sce, colour_by = "cellTypes") +
  theme(aspect.ratio = 1)
g2 <- plotUMAP(mibi.sce, colour_by = "cellTypes_group") +
  theme(aspect.ratio = 1)
g3 <- plotUMAP(mibi.sce, colour_by = "SampleID") +
  theme(aspect.ratio = 1)

grid.arrange(g1, g2, g3, ncol = 2)
```



Cell type composition 

```{r fig.height=8}
df_mibi <- data.frame(colData(mibi.sce))

g1 <- ggplot(df_mibi, aes(x = SampleID, fill = cellTypes)) +
  geom_bar() +
  theme_bw() +
  scale_fill_manual(values = cellTypes_mibi_color) +
  theme(legend.position = "right")

g2 <- ggplot(df_mibi, aes(x = SampleID, fill = cellTypes_group)) +
  geom_bar() +
  theme_bw() +
  scale_fill_manual(values = cellTypes_group_mibi_color) +
  theme(legend.position = "right")

grid.arrange(g1, g2, ncol = 2)
```


## Jackson et al.

```{r eval = FALSE}
source("basel_preprocessing.R")
```

```{r}
sc_mat <- readRDS("../../sc-targeted-proteomics/output/basel_sc_mat.rds")
pg <- readRDS("../../sc-targeted-proteomics/output/basel_pg.rds")
meta <- readRDS("../../sc-targeted-proteomics/output/basel_meta.rds")
selected_chanel <- readRDS("../../sc-targeted-proteomics/output/basel_selected_chanel.rds")
dim(sc_mat)


sc_mat_norm <- apply(sc_mat, 2, scale)
```


```{r eval = FALSE}
umap <- uwot::umap(sc_mat_norm[, selected_chanel])
saveRDS(umap, file = "../../sc-targeted-proteomics/output/basel_umap.rds")
```


```{r}
# color for mibi cell types

cellTypes_basel_color <- sort(c(tableau_color_pal("Classic 20")(20),
                                tableau_color_pal("Summer")(5)))
cellTypes_basel_color <- c(cellTypes_basel_color, "black")
names(cellTypes_basel_color) <- c(unique(pg$cluster_name), "Background")
```


Visualising all cells using UMAP

```{r fig.height=8}
basel_umap <- readRDS("../../sc-targeted-proteomics/output/basel_umap.rds")
library(scattermore)

pg$UMAP1 <- basel_umap[, 1]
pg$UMAP2 <- basel_umap[, 2]
g1 <- ggplot(pg, aes(x = UMAP1, y = UMAP2, color = cluster_name)) + 
  geom_scattermore() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = cellTypes_basel_color) +
  labs(color = "Cell Type")
g1

g2 <- ggplot(pg, aes(x = UMAP1, y = UMAP2, color = cluster_type)) + 
  geom_scattermore() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_tableau() +
  labs(color = "Cell Type")
g2
```


Cell type composition 

```{r fig.height=8}
df_basel <- data.frame(pg)

g1 <- ggplot(df_basel, aes(x = core, fill = cluster_name)) +
  geom_bar() +
  theme_bw() +
  scale_fill_manual(values = cellTypes_basel_color) +
  theme(legend.position = "right",
        axis.text.x = element_blank())
g1

g2 <- ggplot(df_basel, aes(x = core, fill = cluster_type)) +
  geom_bar() +
  theme_bw() +
  scale_fill_tableau() +
  theme(legend.position = "right",
        axis.text.x = element_blank())
g2
```



# Overlapped features between two datasets

```{r}
# intersect(colnames(sc_mat), rownames(mibi.sce))
# colnames(sc_mat)[!colnames(sc_mat) %in% rownames(mibi.sce)]
rownames(mibi.sce)[!rownames(mibi.sce) %in% colnames(sc_mat)]
rownames(mibi.sce)[rownames(mibi.sce) == "phospho-S6"] <- "pS6"
rownames(mibi.sce)[rownames(mibi.sce) == "CD31"] <- "vWF"
rownames(mibi.sce)[rownames(mibi.sce) == "Pan-Keratin"] <- "panCK"
common_anti <- intersect(colnames(sc_mat), rownames(mibi.sce))
cat("Common protein between two datasets")
common_anti
length(common_anti) 
```

```{r}
mibi_exprs <- assay(mibi.sce, "mibi_exprs")
mibi_exprs_common <- mibi_exprs[common_anti, ]
sc_mat_common <- t(sc_mat_norm[, common_anti])
```

```{r eval = FALSE}
umap_common <- uwot::umap(t(sc_mat_common))
saveRDS(umap_common, file = "../../sc-targeted-proteomics/output/basel_umap_common.rds")

umap_mibi_common <- uwot::umap(t(mibi_exprs_common))
saveRDS(umap_mibi_common, file = "../../sc-targeted-proteomics/output/mibi_umap_common.rds")
```


```{r}
basel_umap_common <- readRDS("../../sc-targeted-proteomics/output/basel_umap_common.rds")

pg$UMAP1_common <- basel_umap_common[, 1]
pg$UMAP2_common <- basel_umap_common[, 2]
g1 <- ggplot(pg, aes(x = UMAP1_common, y = UMAP2_common, color = cluster_name)) + 
  geom_scattermore() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = cellTypes_basel_color) +
  labs(color = "Cell Type")
g1

g2 <- ggplot(pg, aes(x = UMAP1_common, y = UMAP2_common, color = cluster_type)) + 
  geom_scattermore() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_tableau() +
  labs(color = "Cell Type")

g2
```



```{r}
mibi_umap_common <- readRDS("../../sc-targeted-proteomics/output/mibi_umap_common.rds")

df_mibi$UMAP1_common <- mibi_umap_common[, 1]
df_mibi$UMAP2_common <- mibi_umap_common[, 2]
g1 <- ggplot(df_mibi, aes(x = UMAP1_common, y = UMAP2_common, color = cellTypes)) + 
  geom_scattermore() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_manual(values = cellTypes_mibi_color) +
  labs(color = "Cell Type")
g1

g2 <- ggplot(df_mibi, aes(x = UMAP1_common, y = UMAP2_common, color = cellTypes_group)) + 
  geom_scattermore() +
  theme_bw() +
  theme(aspect.ratio = 1) +
  scale_color_tableau() +
  labs(color = "Cell Type")

g2
```

# Spatial Pattern Analysis

Here we will use two images from Keren et al. and Jackson et al. as examples to show the image extraction procedure (The full image extraction codes are provided in `mibi_spatial_analysis.R` and `basel_spatial_analysis.R`).

## Keren et al.

```{r}
tiff_name_list <- list.files("../../sc-targeted-proteomics/data/TNBC_shareCellData/", pattern = ".tiff")
tiff_name_list <- tiff_name_list[-24] #filter p30

tiff_name_list
```





Here we are extracting the spatial pattern features from `p1_labeledcellData.tiff`.

```{r}
s <- 1

str_name <- paste("../../sc-targeted-proteomics/data/TNBC_shareCellData/", tiff_name_list[s], sep = "")

sample_id <- as.numeric(gsub("p", "", gsub("_labeledcellData.tiff", "", tiff_name_list[s])))

cat(paste0("Reading the tiff ", print(tiff_name_list[s])))

# read tiff data using raster
r <- raster(str_name)
r


p_sce <- mibi.sce[, mibi.sce$SampleID == sample_id]


# matching the cell label in SingleCellExperiment with the raster position
cell_label <- raster::values(r)
all_group_info <- p_sce$cellTypes_group
notInLabel <- unique(cell_label[!cell_label %in% p_sce$cellLabelInImage])
new_values <- mapvalues((cell_label), from = notInLabel, to = rep("Background",
                                                                  length(notInLabel)))
new_values <- mapvalues((new_values), from = p_sce$cellLabelInImage, to = all_group_info)


new_values_cellTypes <- mapvalues((cell_label), from = notInLabel, to = rep("Background",
                                                                            length(notInLabel)))
new_values_cellTypes <- mapvalues((new_values_cellTypes), from = p_sce$cellLabelInImage, to = p_sce$cellTypes)
```


```{r fig.height=8}

ddf <- rasterToPoints(r)
ddf <- data.frame(ddf)
colnames(ddf) <- c("X", "Y", "value")
ddf$cellType_group <- new_values
ddf$cellType <- new_values_cellTypes
g_cellGroup <- ggplot(NULL) + 
  geom_raster(data = ddf, aes(X, Y, fill = as.factor(cellType_group))) +
  theme_minimal() +
  scale_fill_manual(values = cellTypes_group_mibi_color) +
  coord_quickmap() +
  theme(aspect.ratio = 1, legend.position = "right") +
  labs(fill = "Cell Type")

g_cellTypes <- ggplot(NULL) + 
  geom_raster(data = ddf, aes(X, Y, fill = as.factor(cellType))) +
  theme_minimal() +
  scale_fill_manual(values = cellTypes_mibi_color) +
  coord_quickmap() +
  theme(aspect.ratio = 1, legend.position = "right") +
  labs(fill = "Cell Type")

grid.arrange(g_cellGroup, g_cellTypes, ncol = 2)
```


```{r}
# extract the location and identify the cell centroid
coord_r <- rasterToPoints(r)
center_r_x <- aggregate(coord_r[, 1], list(coord_r[, 3]), median)
group <- center_r_x$Group.1
center_r_x <- center_r_x$x
center_r_y <- aggregate(coord_r[, 2], list(coord_r[, 3]), median)$x
center_r <- data.frame(x = center_r_x, y = center_r_y, group = group)



## maping the cell types to the raster
r_cellType_group <- mapvalues((center_r$group), from = notInLabel, to = rep(0, length(notInLabel)))
r_cellType_group <- mapvalues((r_cellType_group), from = p_sce$cellLabelInImage, to = all_group_info)

center_r$cellTypes <- r_cellType_group

r_cellType <- mapvalues((center_r$group), from = notInLabel, to = rep(0, length(notInLabel)))
r_cellType <- mapvalues((r_cellType), from = p_sce$cellLabelInImage, to = p_sce$cellTypes)

center_r$cellTypes2 <- r_cellType

# filter the center info without cells 
center_r <- center_r[center_r$cellTypes != "0", ]



r_cellType_group <- mapvalues((center_r$group), 
                              from = notInLabel, 
                              to = rep(0, length(notInLabel)))

exprsMat <- assay(p_sce, "mibi_exprs")
exprsMat_map <- sapply(rownames(exprsMat), function(x) {
  zero_one_scale(mapvalues((r_cellType_group), 
                           from = p_sce$cellLabelInImage, 
                           to = exprsMat[x, ]))
  
})
```


```{r}
# create ppp object and extract spatial features
cell_points <- ppp(x = center_r[, 1], y = center_r[, 2], check = FALSE,
                   yrange = c(0, 2048), xrange = c(0, 2048),
                   marks = as.factor(center_r$cellTypes))


plot(density(split(cell_points), sigma = 20), ribbon = FALSE)

idx <- center_r$cellTypes == "Tumour"
cell_points_tumour <- ppp(x = center_r[idx, 1], y = center_r[idx, 2], check = FALSE,
                          yrange = c(0, 2048), xrange = c(0, 2048))

idx <- center_r$cellTypes == "Micro-environment"
cell_points_immune <- ppp(x = center_r[idx, 1], y = center_r[idx, 2], check = FALSE,
                          yrange = c(0, 2048), xrange = c(0, 2048))



ann_tumour_k1 <- mean(nndist(cell_points_tumour, k = 1))
ann_tumour_k3 <- mean(nndist(cell_points_tumour, k = 3))
ann_tumour_k5 <- mean(nndist(cell_points_tumour, k = 5))
ann_tumour_k10 <- mean(nndist(cell_points_tumour, k = 10))

ann_immune_k1 <- mean(nndist(cell_points_immune, k = 1))
ann_immune_k3 <- mean(nndist(cell_points_immune, k = 3))
ann_immune_k5 <- mean(nndist(cell_points_immune, k = 5))
ann_immune_k10 <- mean(nndist(cell_points_immune, k = 10))


E_pcf_cross <- envelope(cell_points, pcfcross, nsim = 100, 
                        correction = "Ripley", savefuns = T,
                        global = TRUE,
                        r = seq(0,250, 10))


E_pcf_tumour <- envelope(cell_points[cell_points$marks == 'Tumour'], pcf, nsim = 100, 
                         correction = "Ripley", savefuns = T,
                         global = TRUE,
                         r = seq(0,250, 10))

E_pcf_immune <- envelope(cell_points[cell_points$marks == "Micro-environment"], pcf, nsim = 100, 
                         correction = "Ripley", savefuns = T,
                         global = TRUE,
                         r = seq(0,250, 10))

```


Patial correlation function for tumour-tumour cells, immune-immune cells and tumour-immune cells
```{r}
par(mfrow = c(2, 2))
plot(E_pcf_tumour)
plot(E_pcf_immune)
plot(E_pcf_cross)
```


```{r}
pcf_results <- c(extract_pcf_results(E_pcf_cross, "cross"),
                 extract_pcf_results(E_pcf_tumour, "tumour"),
                 extract_pcf_results(E_pcf_immune, "immune"))

library(SpatEntropy)
shZ <- shannonX(marks(cell_points))

#Leibovici’s entropy
dmat <- pairdist(cell_points)
dmat[lower.tri(dmat,diag = TRUE)] <- NA
adjmat <- adj_mat(dmat, dd0 = 0, dd1 = 20)
leib <- leibovici(marks(cell_points), adjmat, ordered = TRUE)

leib_freq <- leib$freq.table$proportion
names(leib_freq) <- paste("leib", leib$freq.table$couple, "freq", sep = "_")
leib_entro <- leib$entropy
names(leib_entro) <- "leib_entropy"

intensity_res <- intensity(cell_points)
names(intensity_res) <- paste("intensity", names(intensity_res))


marks(cell_points) <- center_r$cellTypes2
#Leibovici’s entropy
dmat <- pairdist(cell_points)
dmat[lower.tri(dmat,diag = TRUE)] <- NA
adjmat <- adj_mat(dmat, dd0 = 0, dd1 = 20)
leib <- leibovici(marks(cell_points), adjmat, ordered = TRUE)
leib_entro2 <- leib$entropy
names(leib_entro2) <- "leib_entropy_cellTypes"




res_image <- c(intensity_res, shannon = shZ$shannon, leib_entro, leib_entro2, 
               pcf_results,
               ann_tumour_k1 = ann_tumour_k1, ann_tumour_k3 = ann_tumour_k3, 
               ann_tumour_k5 = ann_tumour_k5, ann_tumour_k10 = ann_tumour_k10,
               ann_immune_k1 = ann_immune_k1, ann_immune_k3 = ann_immune_k3, 
               ann_immune_k5 = ann_immune_k5, ann_immune_k10 = ann_immune_k10)

cat(paste0("Features extracted for", tiff_name_list[s]))
round(res_image, 2)
```


## Jackson et al.

The similar analysis for Jackson et al. Basel cohort

```{r}
pg$cluster_type2 <- pg$cluster_type
pg$cluster_type2[pg$cluster_type2 %in% c("Endothelial", "Stromal", "Immune")] <- "Micro-environment"
pg$cluster_type2[pg$cluster_type2 %in% c("Epithelial")] <- "Tumour"
table(pg$cluster_type2)
cellTypes_group_basel_color <- tableau_color_pal("Tableau 10")(length(unique(pg$cluster_type2)))
cellTypes_group_basel_color <- c(cellTypes_group_basel_color, "black")
names(cellTypes_group_basel_color) <- c(unique(pg$cluster_type2), "Background")
```



```{r}

tiff_name_list <- list.files("../../sc-targeted-proteomics/data/Nature_cytof/OMEnMasks/Basel_Zuri_masks/", pattern = "Basel")
map_names <- readRDS("../../sc-targeted-proteomics/output/basel_map_file_core_names.rds")


filter_idx <- c(93, 106, 107, 238, 251, 370, 371)

tiff_name_list <- tiff_name_list[-filter_idx]

s <- 333
str_name <- paste("../../sc-targeted-proteomics/data/Nature_cytof/OMEnMasks/Basel_Zuri_masks/", 
                  tiff_name_list[s], sep = "")

r <- raster(str_name)
cell_label <- raster::values(r)

ncells <- length(unique(cell_label)) - 1

sample_id <- names(which(map_names[, 2] == tiff_name_list[s]))

idx <- which(pg$core == sample_id)

pg_sub <- pg[idx, ]
sc_mat_subset <- sc_mat[idx, ]
```


```{r}
all_group_info <- pg_sub$cluster_type2

cell_label <- mapvalues(cell_label, 
                        from = sort(unique(cell_label[cell_label != 0])),
                        to = seq_len(length(unique(cell_label[cell_label != 0]))))
values(r) <- cell_label

new_values <- mapvalues(cell_label, from = 0, to = "Background")

new_values <- mapvalues(new_values, from = seq_len(length(unique(cell_label[cell_label != 0]))), to = all_group_info)


ddf <- rasterToPoints(r)
ddf <- data.frame(ddf)
colnames(ddf) <- c("X", "Y", "value")
ddf$cellType <- new_values
g_cellTypes <- ggplot(NULL) + 
  geom_raster(data = ddf, aes(X, Y, fill = as.factor(cellType))) +
  theme_minimal() +
  scale_fill_manual(values = cellTypes_group_basel_color) +
  coord_quickmap() +
  theme(aspect.ratio = 1) +
  labs(fill = "Cell Type")



new_values2 <- mapvalues(cell_label, from = 0, to = "Background")

new_values2 <- mapvalues(new_values2, from = seq_len(length(unique(cell_label[cell_label != 0]))), to = pg_sub$cluster_name)


ddf$cellType2 <- new_values2
g_cellTypes2 <- ggplot(NULL) + 
  geom_raster(data = ddf, aes(X, Y, fill = as.factor(cellType2))) +
  theme_minimal() +
  scale_fill_manual(values = cellTypes_basel_color) +
  coord_quickmap() +
  theme(aspect.ratio = 1) +
  labs(fill = "Cell Type")


grid.arrange(g_cellTypes, g_cellTypes2, nrow = 2)
```


```{r}
coord_r <- rasterToPoints(r)
center_r_x <- aggregate(coord_r[, 1], list(coord_r[, 3]), median)
group <- center_r_x$Group.1
center_r_x <- center_r_x$x
center_r_y <- aggregate(coord_r[, 2], list(coord_r[, 3]), median)$x

center_r <- data.frame(x = center_r_x, y = center_r_y, group = group)


center_r <- center_r[center_r$group != 0, ]

center_r$cellTypes <- pg_sub$cluster_type2

center_r$cellTypes2 <- pg_sub$cluster_type


library(sf)
library(maptools)


cell_points <- ppp(x = center_r[, 1], y = center_r[, 2], check = FALSE,
                   yrange = c(0, round(max(coord_r[, 2]))), 
                   xrange = c(0, round(max(coord_r[, 1]))),
                   marks = as.factor(center_r$cellTypes))



plot(density(split(cell_points), sigma = 20), ribbon = FALSE)

idx <- center_r$cellTypes == "Tumour"
cell_points_tumour <- ppp(x = center_r[idx, 1], y = center_r[idx, 2], check = FALSE,
                          yrange = c(0, round(max(coord_r[, 2]))), 
                          xrange = c(0, round(max(coord_r[, 1]))))

idx <- center_r$cellTypes == "Micro-environment"
cell_points_immune <- ppp(x = center_r[idx, 1], y = center_r[idx, 2], check = FALSE,
                          yrange = c(0, round(max(coord_r[, 2]))), 
                          xrange = c(0, round(max(coord_r[, 1]))))

ann_tumour_k1 <- mean(nndist(cell_points_tumour, k = 1))
ann_tumour_k3 <- mean(nndist(cell_points_tumour, k = 3))
ann_tumour_k5 <- mean(nndist(cell_points_tumour, k = 5))
ann_tumour_k10 <- mean(nndist(cell_points_tumour, k = 10))

ann_immune_k1 <- mean(nndist(cell_points_immune, k = 1))
ann_immune_k3 <- mean(nndist(cell_points_immune, k = 3))
ann_immune_k5 <- mean(nndist(cell_points_immune, k = 5))
ann_immune_k10 <- mean(nndist(cell_points_immune, k = 10))


E_pcf_cross <- envelope(cell_points, pcfcross, nsim = 100, 
                        correction = "Ripley", savefuns = T,
                        global = TRUE,
                        r = seq(0,250, 10))


E_pcf_tumour <- envelope(cell_points[cell_points$marks=='Tumour'], pcf, nsim = 100, 
                         correction = "Ripley", savefuns = T,
                         global = TRUE,
                         r = seq(0,250, 10))

E_pcf_immune <-envelope(cell_points[cell_points$marks=="Micro-environment"], pcf, nsim = 100, 
                        correction = "Ripley", savefuns = T,
                        global = TRUE,
                        r = seq(0,250, 10))


par(mfrow = c(2, 2))
plot(E_pcf_tumour)
plot(E_pcf_immune)
plot(E_pcf_cross)


par(mfrow = c(1, 1))


pcf_results <- c(extract_pcf_results(E_pcf_cross, "cross"),
                 extract_pcf_results(E_pcf_tumour, "tumour"),
                 extract_pcf_results(E_pcf_immune, "immune"))

library(SpatEntropy)
shZ <- shannonX(marks(cell_points))

#Leibovici’s entropy
dmat <- pairdist(cell_points)
dmat[lower.tri(dmat,diag=TRUE)] <- NA
adjmat <- adj_mat(dmat, dd0 = 0, dd1 = 20)
leib <- leibovici(marks(cell_points), adjmat, ordered=T)

leib_freq <- leib$freq.table$proportion
names(leib_freq) <- paste("leib", leib$freq.table$couple, "freq", sep = "_")
leib_entro <- leib$entropy
names(leib_entro) <- "leib_entropy"

intensity_res <- intensity(cell_points)
if (length(intensity_res) < 2) {
  tab <- table(marks(cell_points))
  max_name <- names(tab)[which.max(tab)]
  min_name <- names(tab)[which.min(tab)]
  intensity_res <- c(intensity_res, 0)
  names(intensity_res) <- c(paste("intensity", max_name),
                            paste("intensity", min_name))
  
} else {
  names(intensity_res) <- paste("intensity", names(intensity_res))
}



marks(cell_points) <- center_r$cellTypes
#Leibovici’s entropy
dmat <- pairdist(cell_points)
dmat[lower.tri(dmat,diag=TRUE)] <- NA
adjmat <- adj_mat(dmat, dd0 = 0, dd1 = 20)
leib <- leibovici(marks(cell_points), adjmat, ordered=T)
leib_entro2 <- leib$entropy
names(leib_entro2) <- "leib_entropy_cellTypes"




res_image <- c(intensity_res, shannon = shZ$shannon, leib_entro, leib_entro2, 
               pcf_results,
               ann_tumour_k1 = ann_tumour_k1, ann_tumour_k3 = ann_tumour_k3, 
               ann_tumour_k5 = ann_tumour_k5, ann_tumour_k10 = ann_tumour_k10,
               ann_immune_k1 = ann_immune_k1, ann_immune_k3 = ann_immune_k3, 
               ann_immune_k5 = ann_immune_k5, ann_immune_k10 = ann_immune_k10)
res_image

```

